Intro Seminar

### 2017-03-12 doc/seminar2017.Rmd
eGFR is not lower in people with DM

```{r hyperfiltration}
ds %>% 
  dplyr::filter(eGFR < 45) %>% 
  dplyr::select(SID, VN, Age, eGFR, dm_status, acr_status)

ds %>% 
  scatter_plot("Age", "eGFR",
               "Age", "eGFR")
```

>>>>

```{r hyperfiltration}
ds %>% 
  dplyr::filter(eGFR < 45) %>% 
  dplyr::select(SID, VN, Age, eGFR, dmStatus, acrStatus)

ds %>% 
  scatter_plot("Age", "eGFR",
               "Age", "eGFR")

ds %>% 
  dplyr::select(dmStatus, eGFR, fVN) %>% 
  na.omit() %>% 
  box_plot("dmStatus", "eGFR",
               "Diabetic Status", "eGFR",
           facet = TRUE)
```
